\documentclass{article}
\author{Keith Evan Schubert}
\title{Advent 2009}
\begin{document}
\maketitle

\section{Week 1}
November 29

\subsection{AM}
  Jesus in the Creation - Why was it good?  Why did the Father give us? John 6:35-45, 17:2  Note that this involves work on the Son's part - John 6:35-45, 8:42  Why did the Son accept?  Matthew 18:7-14 This is probably not obvious, but Jesus mentions that the angels that watch over the elect always face the Father.  You see the Father in the gift.  It is a intimate act of love to watch the Father's adopted children.  How much more to receive the gift?  No angel could save us, showing off Jesus par excelance (Revelation 5).  But even more important to Jesus was joy and intimacy with the Father in doing this.

\subsection{PM}  Why make a people?  Why the patriarchs?  Why make a covenant?  Why Abraham and David but not Moses?

\section{Week 2}
December 6

\subsection{AM}  Why a babe in a manger?  Why Mary and Joseph?  Why did He have a childhood and work? DD

\subsection{PM}  Why so long?  2k years from Abraham, 1.5k years from Moses, 1k year from David

Genesis 2:16-17  That day you will die

Genesis 6:1-6    God won't contend with man forever

Genesis 15:12-16  400 years so Amorite's sin is full

Matthew 23:27-33   Pharisees fill up father's sins

I Thessalonians 2:13-16  Preventing others from hearing fills up sin

Jeremiah 12:1-6   tired because of sin (sin makes time longer)

Psalm 95   Forty years with sinners is long

Habakkuk 1:1-4  How long till God judges?

Zechariah 1:7-17  How long till God forgives?

Luke 18:1-8  Unjust judge

II Peter 2,3   long time, God isn't slack, he is saving elect.

Hebrews 4:1-10  long time - God's salvation

I Corinthians 13:4  love suffers long

Isaiah 65:17-25  long time new heavens

Deuteronomy 31:11-13   Children that have not seen





\section{Week 3}
December 13

\subsection{AM}  Why the bride/church?

Man's insignificance:

Hebrews 1, Psalm 8 What is man?

Isaiah 49:6 It is too small a thing

Marriage feast:

Matthew 22



Church as the bride:

Ephesians 5

Revelation 19

Revelation 21

\subsection{PM}  Why not everyone?
Romans 9








\section{Week 4}
December 20

\subsection{AM}  Songs and Scripture  - Why do we celebrate?

\subsection{PM}  Why the angles singing?  Dark day on Sinai and a bright night in Bethlehem.  Heb 12 DD

\end{document} 