Ge 3:15  And I will put enmity between you and the woman, and between your seed and her seed; it shall bruise your head, and you shall bruise his heel.
Ge 12:3  And I will bless them that bless you, and curse him that curses you: and in you shall all families of the earth be blessed.
Ge 49:10  The scepter shall not depart from Judah, nor a lawgiver from between his feet, until Shiloh come; and to him shall the gathering of the people be.
De 18:15  The LORD your God will raise up to you a Prophet from the middle of you, of your brothers, like to me; to him you shall listen;
Ps 2:2  The kings of the earth set themselves, and the rulers take counsel together, against the LORD, and against his anointed, saying,
Ps 45:2  You are fairer than the children of men: grace is poured into your lips: therefore God has blessed you for ever.
Ps 68:18  You have ascended on high, you have led captivity captive: you have received gifts for men; yes, for the rebellious also, that the LORD God might dwell among them.
Ps 69:21  They gave me also gall for my meat; and in my thirst they gave me vinegar to drink.
Ps 110:1  The LORD said to my Lord, Sit you at my right hand, until I make your enemies your footstool.
Ps 118:22  The stone which the builders refused is become the head stone of the corner.
Ps 132:11  The LORD has sworn in truth to David; he will not turn from it; Of the fruit of your body will I set on your throne.
Isa 2:4  And he shall judge among the nations, and shall rebuke many people: and they shall beat their swords into plowshares, and their spears into pruning hooks: nation shall not lift up sword against nation, neither shall they learn war any more.
Isa 7:14  Therefore the Lord himself shall give you a sign; Behold, a virgin shall conceive, and bear a son, and shall call his name Immanuel.
Isa 9:2  The people that walked in darkness have seen a great light: they that dwell in the land of the shadow of death, on them has the light shined.
Isa 9:7  Of the increase of his government and peace there shall be no end, on the throne of David, and on his kingdom, to order it, and to establish it with judgment and with justice from now on even for ever. The zeal of the LORD of hosts will perform this.
Isa 11:10  And in that day there shall be a root of Jesse, which shall stand for an ensign of the people; to it shall the Gentiles seek: and his rest shall be glorious.
Isa 25:8  He will swallow up death in victory; and the Lord GOD will wipe away tears from off all faces; and the rebuke of his people shall he take away from off all the earth: for the LORD has spoken it.
Isa 28:16  Therefore thus said the Lord GOD, Behold, I lay in Zion for a foundation a stone, a tried stone, a precious corner stone, a sure foundation: he that believes shall not make haste.
Isa 42:1  Behold my servant, whom I uphold; my elect, in whom my soul delights; I have put my spirit on him: he shall bring forth judgment to the Gentiles.
Isa 49:6  And he said, It is a light thing that you should be my servant to raise up the tribes of Jacob, and to restore the preserved of Israel: I will also give you for a light to the Gentiles, that you may be my salvation to the end of the earth.
Isa 52:14  As many were astonished at you; his visage was so marred more than any man, and his form more than the sons of men:
Isa 53:2  For he shall grow up before him as a tender plant, and as a root out of a dry ground: he has no form nor comeliness; and when we shall see him, there is no beauty that we should desire him.
Isa 55:4  Behold, I have given him for a witness to the people, a leader and commander to the people.
Isa 59:16  And he saw that there was no man, and wondered that there was no intercessor: therefore his arm brought salvation to him; and his righteousness, it sustained him.
Isa 61:1  The Spirit of the Lord GOD is on me; because the LORD has anointed me to preach good tidings to the meek; he has sent me to bind up the brokenhearted, to proclaim liberty to the captives, and the opening of the prison to them that are bound;
Isa 62:11  Behold, the LORD has proclaimed to the end of the world, Say you to the daughter of Zion, Behold, your salvation comes; behold, his reward is with him, and his work before him.
Isa 63:1  Who is this that comes from Edom, with dyed garments from Bozrah?  this that is glorious in his apparel, traveling in the greatness of his strength? I that speak in righteousness, mighty to save.
Jer 23:5  Behold, the days come, said the LORD, that I will raise to David a righteous Branch, and a King shall reign and prosper, and shall execute judgment and justice in the earth.
Eze 17:22  Thus said the Lord GOD; I will also take of the highest branch of the high cedar, and will set it; I will crop off from the top of his young twigs a tender one, and will plant it on an high mountain and eminent:
Da 2:34  You saw till that a stone was cut out without hands, which smote the image on his feet that were of iron and clay, and broke them to pieces.
Da 2:44  And in the days of these kings shall the God of heaven set up a kingdom, which shall never be destroyed: and the kingdom shall not be left to other people, but it shall break in pieces and consume all these kingdoms, and it shall stand for ever.
Da 7:13  I saw in the night visions, and, behold, one like the Son of man came with the clouds of heaven, and came to the Ancient of days, and they brought him near before him.
Da 9:25  Know therefore and understand, that from the going forth of the commandment to restore and to build Jerusalem to the Messiah the Prince shall be seven weeks, and three score and two weeks: the street shall be built again, and the wall, even in troublous times.
Mic 5:2  But you, Bethlehem Ephratah, though you be little among the thousands of Judah, yet out of you shall he come forth to me that is to be ruler in Israel; whose goings forth have been from of old, from everlasting.
Hag 2:7  And I will shake all nations, and the desire of all nations shall come: and I will fill this house with glory, said the LORD of hosts.
Zec 3:8  Hear now, O Joshua the high priest, you, and your fellows that sit before you: for they are men wondered at: for, behold, I will bring forth my servant the BRANCH.
Zec 6:12  And speak to him, saying, Thus speaks the LORD of hosts, saying, Behold the man whose name is The BRANCH; and he shall grow up out of his place, and he shall build the temple of the LORD:
Zec 9:9  Rejoice greatly, O daughter of Zion; shout, O daughter of Jerusalem: behold, your King comes to you: he is just, and having salvation; lowly, and riding on an ass, and on a colt the foal of an ass.
Zec 11:12  And I said to them, If you think good, give me my price; and if not, forbear. So they weighed for my price thirty pieces of silver.
Zec 12:10  And I will pour on the house of David, and on the inhabitants of Jerusalem, the spirit of grace and of supplications: and they shall look on me whom they have pierced, and they shall mourn for him, as one mourns for his only son, and shall be in bitterness for him, as one that is in bitterness for his firstborn.
Zec 13:7  Awake, O sword, against my shepherd, and against the man that is my fellow, said the LORD of hosts: smite the shepherd, and the sheep shall be scattered: and I will turn my hand on the little ones.
Mal 3:1  Behold, I will send my messenger, and he shall prepare the way before me: and the LORD, whom you seek, shall suddenly come to his temple, even the messenger of the covenant, whom you delight in: behold, he shall come, said the LORD of hosts. 