\chapter{Reformation Day}\label{c-reformationday}  The Solas of the Reformation  Today is October 31, and while to most people this means celebrating the pagan holiday of Samhain (pronounced Sow-in), under the name Halloween.  For my commentary on what the false holidays not to celebrate, see Appendix~\ref{a-nohalloween}.  This is reformation day.On this day in 1517, Martin Luther Nailed the 95 Thesis on the Church door of Wittenberg.  The Protestant Reformation was launched.  Why is this so dear to us?  To answer this we have to see what the fight was over.  Many different formulas exist, but I will use the one that they used, the solas.  Sola is Latin for only or alone.  The solas are: \begin{enumerate}\item Sola Scriptura - Scripture Alone\item Sola Fide - Faith Alone\item Sola Gratia - Grace Alone\item Solo Christo - Christ Alone\item Soli Deo Gloria - To God's Glory Alone\end{enumerate}I have chosen this order to emphasize the two main points of the reformation: the formal cause (Sola Scriptura) and the material cause (Sola Fide).A formal cause is the one which outlines or plans what is to be - it describes the form of things.  Protestants believe that only the Bible fits this bill.  It alone is binding on the conscience.  Let's look at some Scripture:\begin{quote}But {\bf thou} hast been thoroughly acquainted with my teaching, conduct, purpose, faith, longsuffering, love, endurance, persecutions, sufferings: what sufferings happened to me in Antioch, in Iconium, in Lystra; what persecutions I endured; and the Lord delivered me out of all. And all indeed who desire to live piously in Christ Jesus will be persecuted. But wicked men and juggling impostors shall advance in evil, leading and being led astray. But {\bf thou}, abide in those things which thou hast learned, and of which thou hast been fully persuaded, knowing of whom thou hast learned them; and that from a child thou hast known the sacred letters, which are able to make thee wise unto salvation, through faith which is in Christ Jesus. Every scripture is divinely inspired, and profitable for teaching, for conviction, for correction, for instruction in righteousness; that the man of God may be complete, fully fitted to every good work. I testify before God and Christ Jesus, who is about to judge living and dead, and by his appearing and his kingdom, proclaim the word; be urgent in season and out of season, convict, rebuke, encourage, with all longsuffering and doctrine. For the time shall be when they will not bear sound teaching; but according to their own lusts will heap up to themselves teachers, having an itching ear; and they will turn away their ear from the truth, and will have turned aside to fables. But {\bf thou}, be sober in all things, bear evils, do the work of an evangelist, fill up the full measure of thy ministry. For *I* am already being poured out, and the time of my release is come. I have combated the good combat, I have finished the race, I have kept the faith. Henceforth the crown of righteousness is laid up for me, which the Lord, the righteous Judge, will render to me in that day; but not only to me, but also to all who love his appearing.\begin{flushright} 2 Timothy 3:10-4:8 \end{flushright} \end{quote}1 Peter 1:20-2:3Isaiah 55:6-13A material cause is one of which the whole thing is made up.  In the case against the Roman Church, that was its denial of true salvation.  We are salved by faith alone:Romans 3:19-4:16Galatians 2:10-3:18Grace aloneEphesians 2Christ aloneJohn 20:31, 1 John 5:13God's GloryEphesians 1