\chapter{Thanksgiving}

Thanksgiving is one of the best gifts our country has given to the world.  Fall festivals celebrate the bounty of what we have, while Thanksgiving focuses on the giver, God.  Thanksgiving is a uniquely God centered idea.  Your average person thinks that Thanksgiving is about food and family.  Both are there, to be certain, but this is not what it is about.  Don't confuse the ones with celebrate with, and the trimmings of the celebration, with the object of the celebration.  That would be like saying parties are about cake and presents, rather than the person having the birthday.

I have always had a liking for this holiday, but I have never felt I celebrated it right.  A number of years ago my brilliant wife came up with the first major transformation of this day for us, she started having each of us scrapbook what we were thankful for. In order to do this we had to think about it and look through pictures of what God had granted us, and how he had shepherded us.  It is now my favorite tradition.  Then a few years ago, my family decided we wanted to decorate and start increasing our sense and appreciation.  I have always loved candles and sparkly things, and I found this cool fall tree like candle holder with little sparkly gems hung from its branches.  It was like a fall oak Christmas tree, with five tea lite holders.  I figured I could use it as part of thanksgiving but had no idea of how.

A few weeks ago I was thinking about how to make family worship more consistent in our family and I realized that during the holidays, our kids looked forward to family worship, even reminding us to do it.  No guilt, just joy.  It brought up this study which I have been working on for years, and I knew I needed to be more serious.  We went one Saturday to our local Hobby Lobby to look for decorations, as I find the really set a worshipful mood for us.  My wife told us to each pick one thing.  I encouraged the kids to think about what we could use to in worshiping God during Thanksgiving.  I saw this cool wire pumpkin with leaves and a candle, but didn't think my wife would like it so I moved on.  A little later she pointed it out to me and I knew it was something important.  As we walked around picking things up and discussing, this idea came to me.

We would use the Heidelberg Confession's\footnote{While I don't follow a confession, I greatly enjoy reading and learning from them.  I just feel God's Word is the only thing I owe allegiance to.} famous triad Guilt-Grace-Gratitude as a lead in to Thanksgiving.  A heart of gratitude makes for true thankfulness.  I realized that that made four things and it was almost my fall oak.  I originally planned on putting in a week of praise between triple-G and Thanksgiving, but tonight I realized that Guilt makes no sense without an appreciation for God.

%Thus start four Thursdays before Thanksgiving, so Thanksgiving will be the fifth Thursday.  The celebration will be Thursday, Sunday\footnote{Saturday or Sunday would work, I chose Sunday because our Church here in Texas does not have Sunday Evening worship and I miss it.}, and Tuesday.  Each week has a theme, Sriptures, songs, and activities outlined below.

\section{First Day (Tuesday): God}
\noindent Light the top candle.  We light the top candle as God is the greatest, there is none above Him.  As you light the candle read Genesis 1:1-3.

\Scripture{Genesis 1:1-3}{KJV}{
In the beginning God created the heaven and the earth.  And the earth was without form, and void; and darkness was upon the face of the deep. And the Spirit of God moved upon the face of the waters.

And God said, Let there be light: and there was light.}


\noindent Pray together


\noindent Sing \emph{Immortal Invisible}

\inputSong{../songs/Immortal_Invisible.tex}


\noindent Read Revelation 4

\Scripture{Revelation 4}{ESV}{After this I looked, and behold, a door standing open in heaven! And the first voice, which I had heard speaking to me like a trumpet, said, ``Come up here, and I will show you what must take place after this.'' \V{2} At once I was in the Spirit, and behold, a throne stood in heaven, with one seated on the throne. 3 And he who sat there had the appearance of jasper and carnelian, and around the throne was a rainbow that had the appearance of an emerald. \V{4} Around the throne were twenty-four thrones, and seated on the thrones were twenty-four elders, clothed in white garments, with golden crowns on their heads. \V{5} From the throne came flashes of lightning, and rumblings\footnote{or voices, or sounds} and peals of thunder, and before the throne were burning seven torches of fire, which are the seven spirits of God, \V{6} and before the throne there was as it were a sea of glass, like crystal.

And around the throne, on each side of the throne, are four living creatures, full of eyes in front and behind: \V{7} the first living creature like a lion, the second living creature like an ox, the third living creature with the face of a man, and the fourth living creature like an eagle in flight. \V{8} And the four living creatures, each of them with six wings, are full of eyes all around and within, and day and night they never cease to say,

\begin{quote}``Holy, holy, holy, is the Lord God Almighty,
    who was and is and is to come!''
\end{quote}

\V{9} And whenever the living creatures give glory and honor and thanks to him who is seated on the throne, who lives forever and ever, \V{10} the twenty-four elders fall down before him who is seated on the throne and worship him who lives forever and ever. They cast their crowns before the throne, saying,

\begin{quote}\V{11} ``Worthy are you, our Lord and God,
    to receive glory and honor and power,
for you created all things,
    and by your will they existed and were created.''
\end{quote}
}




\noindent Sing \emph{This is my Father's World}

\inputSong{../songs/This_Is_My_Fathers_World.tex}



\noindent Pray together

\subsection{God Knows All Soduku}

Look up a soduku puzzle that is of the appropriate difficulty for your family online (there are tons of sites for this).  Print out a blank soduku for each member of the family and one extra.  On the blanks copy a few of the numbers so everyone has some unique values, and some shared.  You can also give some partial solutions, such as $>4$ for 6 on someone, and even on another, and $<8$ on another.  The extra should have some unique ones also, and in particular some of the partials should require information from the extra.  It should not be possible to solve the soduku from what the have.

Give each person their own soduku sheet, and ask them to solve it.  When they indicate they can't, tell them so to we can't know everything on our own.  Give each a copy of the extra, and explain that God gives us direct revelation in the Bible.

God did not leave us alone, He gave us the Church, so have the family work as a group. They should have some fun working together.  Note, everyone is needed.  We all share some basic truths, but we all can help each other with what God has taught us.  When you put it all together, you should be able to solve it, just like the church with His Word and guidance can lead us to all truth.



%\subsection{Sunday}
%
%
%\noindent Read Revelation 5
%
%\Scripture{Revelation 5}{ESV}{\V{1} Then I saw in the right hand of him who was seated on the throne a scroll written within and on the back, sealed with seven seals. \V{2} And I saw a mighty angel proclaiming with a loud voice, “Who is worthy to open the scroll and break its seals?” \V{3} And no one in heaven or on earth or under the earth was able to open the scroll or to look into it, \V{4} and I began to weep loudly because no one was found worthy to open the scroll or to look into it. \V{5} And one of the elders said to me, “Weep no more; behold, the Lion of the tribe of Judah, the Root of David, has conquered, so that he can open the scroll and its seven seals.”
%
%\V{6} And between the throne and the four living creatures and among the elders I saw a Lamb standing, as though it had been slain, with seven horns and with seven eyes, which are the seven spirits of God sent out into all the earth. \V{7} And he went and took the scroll from the right hand of him who was seated on the throne. \V{8} And when he had taken the scroll, the four living creatures and the twenty-four elders fell down before the Lamb, each holding a harp, and golden bowls full of incense, which are the prayers of the saints. \V{9} And they sang a new song, saying,
%
%\begin{quote}
%``Worthy are you to take the scroll
%    and to open its seals,
%for you were slain, and by your blood you ransomed people for God
%    from every tribe and language and people and nation,
%\V{10} and you have made them a kingdom and priests to our God,
%    and they shall reign on the earth.''
%\end{quote}
%
%\V{11} Then I looked, and I heard around the throne and the living creatures and the elders the voice of many angels, numbering myriads of myriads and thousands of thousands, \V{12} saying with a loud voice,
%
%\begin{quote}
%``Worthy is the Lamb who was slain,
%to receive power and wealth and wisdom and might
%and honor and glory and blessing!''
%\end{quote}
%
%\V{13} And I heard every creature in heaven and on earth and under the earth and in the sea, and all that is in them, saying,
%
%\begin{quote}
%``To him who sits on the throne and to the Lamb
%be blessing and honor and glory and might forever and ever!''
%\end{quote}
%
%\V{14} And the four living creatures said, ``Amen!'' and the elders fell down and worshiped.}
%
%
%Make Folding Craft Stick Canvas of the Cross.  How to Make the Folding Craft Stick Canvas:
%\begin{enumerate}
%\item If you are using the mini-jumbo craft sticks, cut the one-inch masking into 4-inch pieces.
%\item Place two sticks together, side by side, and tape them together covering both the sticks with the tape.
%\item Turn the two sticks over so that they are diagonal to you.
%\item Place another craft stick next to and below the two sticks that you taped together. Use another piece of tape to tape the bottom two sticks together.
%\item Turn all three sticks over diagonally and place another stick at the bottom of the row and tape the last two sticks together. Keep going until you have a whole row of sticks.
%\item You can also cover the first and last stick in the row by placing tape over the stick and then folding it back over the stick. It is easier to write on the tape than the craft stick. The ink soaks into the sticks and blurs.
%\item Draw out your design on the craft stick canvas with a pencil. If you make a mistake, you can erase it. When you are happy with your design paint it with the acrylic paint. When the acrylic paint is dry use a black marker to outline your shapes and write the words.
%\end{enumerate}
%
%\subsection{Tuesday}
%
%\noindent Read John
%



\clearpage
\section{Second Day (Thursday): Guilt}
Guilt has a bad rap in our culture, but guilt does not have to be only negative.  There is a place for guilt in recognizing what Christ did for us and in motivating us to want to be better.

%\subsection{Thursday}
Light the top and bottom candles.

\noindent Read Ephesians 2:1-3

\Scripture{Ephesians 2:1-3}{ESV}{And you were dead in the trespasses and sins \V{2} in which you once walked, following the course of this world, following the prince of the power of the air, the spirit that is now at work in the sons of disobedience—\V{3} among whom we all once lived in the passions of our flesh, carrying out the desires of the body and the mind, and were by nature children of wrath, like the rest of mankind.}

\noindent pray

\noindent Sing \emph{Unworthy}

\inputSong{../songs/Unworthy.tex}

\noindent Read Romans 3:9-20

\Scripture{Romans 3:9-20}{ESV}{\V{9}What then? Are we Jews any better off?  No, not at all. For we have already charged that all, both Jews and Greeks, are under sin, \V{10} as it is written:

``None is righteous, no, not one;

\V{11} 	no one understands;

no one seeks for God.

\V{12} 	All have turned aside; together they have become worthless;

no one does good,

not even one.''

\V{13} 	``Their throat is an open grave;

they use their tongues to deceive.''

“The venom of asps is under their lips.''

\V{14} 	``Their mouth is full of curses and bitterness.''

\V{15} 	``Their feet are swift to shed blood;

\V{16} 	in their paths are ruin and misery,

\V{17} 	and the way of peace they have not known.''

\V{18} 	``There is no fear of God before their eyes.''

\V{19} Now we know that whatever the law says it speaks to those who are under the law, so that every mouth may be stopped, and the whole world may be held accountable to God. \V{20} For by works of the law no human being will be justified in his sight, since through the law comes knowledge of sin.}

\noindent Sing \emph{Psalm 51}

\inputSong{../songs/Psalm51.tex}

\noindent Pray

%\subsection{Sunday}
%
%\noindent Read Romans 5:12-21
%
%\Scripture{Romans 5:12-21}{ESV}{Therefore, just as sin came into the world through one man, and death through sin, and so death spread to all men because all sinned—\V{13} for sin indeed was in the world before the law was given, but sin is not counted where there is no law. \V{14} Yet death reigned from Adam to Moses, even over those whose sinning was not like the transgression of Adam, who was a type of the one who was to come.
%
%\V{15} But the free gift is not like the trespass. For if many died through one man's trespass, much more have the grace of God and the free gift by the grace of that one man Jesus Christ abounded for many. \V{16} And the free gift is not like the result of that one man's sin. For the judgment following one trespass brought condemnation, but the free gift following many trespasses brought justification. \V{17} For if, because of one man's trespass, death reigned through that one man, much more will those who receive the abundance of grace and the free gift of righteousness reign in life through the one man Jesus Christ.
%
%\V{18} Therefore, as one trespass led to condemnation for all men, so one act of righteousness leads to justification and life for all men. \V{19} For as by the one man's disobedience the many were made sinners, so by the one man's obedience the many will be made righteous. \V{20} Now the law came in to increase the trespass, but where sin increased, grace abounded all the more, \V{21} so that, as sin reigned in death, grace also might reign through righteousness leading to eternal life through Jesus Christ our Lord.}

\subsection{Change my ways oh Lord Candles}

Take a one inch long piece of toilet paper and write something you do that you wish you didn't. Fold the paper in half so the text can't be seen and then roll it as tight as possible.  Dip this wick in a briney salt water solution and place on foil.  Put the wicks in the oven at $200^\circ$ for 20 minutes\footnote{or dry overnight}.  While the wicks are drying heat some old wax in a cleaned out soup can placed in a pot surrounded by hot water.  When the wax is melted dip the dry wicks in the wax and remove slowly and place on aluminum foil.  They should be cool in a couple of minutes.  In a regular candle you would keep re-dipping to make them large, but in our case we want smaller candles that burn fairly quickly, so just dip once.

To burn them, pre-drill one hole for each family member in a 1.5 inch wood disk (the size of a tea light).  place each candle in the wood disk and put it in a tea light holder.  Light each candle.


\noindent Read Romans 7

\Scripture{Romans 7}{ESV}{
\V{1} Or do you not know, brothers—for I am speaking to those who know the law—that the law is binding on a person only as long as he lives? \V{2} For a married woman is bound by law to her husband while he lives, but if her husband dies she is released from the law of marriage. \V{3} Accordingly, she will be called an adulteress if she lives with another man while her husband is alive. But if her husband dies, she is free from that law, and if she marries another man she is not an adulteress.

	\V{4} Likewise, my brothers, you also have died to the law through the body of Christ, so that you may belong to another, to him who has been raised from the dead, in order that we may bear fruit for God. \V{5} For while we were living in the flesh, our sinful passions, aroused by the law, were at work in our members to bear fruit for death. \V{6} But now we are released from the law, having died to that which held us captive, so that we serve in the new way of the Spirit and not in the old way of the written code.


	\V{7} What then shall we say? That the law is sin? By no means! Yet if it had not been for the law, I would not have known sin. For I would not have known what it is to covet if the law had not said, “You shall not covet.” \V{8} But sin, seizing an opportunity through the commandment, produced in me all kinds of covetousness. For apart from the law, sin lies dead. \V{9} I was once alive apart from the law, but when the commandment came, sin came alive and I died. \V{10} The very commandment that promised life proved to be death to me. \V{11} For sin, seizing an opportunity through the commandment, deceived me and through it killed me. \V{12} So the law is holy, and the commandment is holy and righteous and good.

	\V{13} Did that which is good, then, bring death to me? By no means! It was sin, producing death in me through what is good, in order that sin might be shown to be sin, and through the commandment might become sinful beyond measure. \V{14} For we know that the law is spiritual, but I am of the flesh, sold under sin. \V{15} For I do not understand my own actions. For I do not do what I want, but I do the very thing I hate. \V{16} Now if I do what I do not want, I agree with the law, that it is good. \V{17} So now it is no longer I who do it, but sin that dwells within me. \V{18} For I know that nothing good dwells in me, that is, in my flesh. For I have the desire to do what is right, but not the ability to carry it out. \V{19} For I do not do the good I want, but the evil I do not want is what I keep on doing. \V{20} Now if I do what I do not want, it is no longer I who do it, but sin that dwells within me.

	\V{21} So I find it to be a law that when I want to do right, evil lies close at hand. \V{22} For I delight in the law of God, in my inner being, \V{23} but I see in my members another law waging war against the law of my mind and making me captive to the law of sin that dwells in my members. \V{24} Wretched man that I am! Who will deliver me from this body of death? \V{25} Thanks be to God through Jesus Christ our Lord! So then, I myself serve the law of God with my mind, but with my flesh I serve the law of sin.}

Pass out candles and light them while singing Psalm 51.



\clearpage
\section{Third Day (Saturday): Grace}

\noindent Light the top candle then the bottom candle, then the second highest.  We light the top candle as God is the greatest, the bottom as our sin is the worst, and the second highest as God's grace reaches down to us.

\Scripture{}{ESV}{
}


\noindent Pray together


\noindent Sing \emph{Amazing Grace}

\inputSong{../songs/Amazing_Grace.tex}


\noindent Read

\Scripture{}{ESV}{}

\noindent Sing \emph{Psalm 51}

\inputSong{../songs/Psalm51.tex}

\noindent Pray

\Scripture{I Timothy 1:12-17}{ESV}{
\V{12} I thank him who has given me strength, Christ Jesus our Lord, because he judged me faithful, appointing me to his service, \V{13} though formerly I was a blasphemer, persecutor, and insolent opponent. But I received mercy because I had acted ignorantly in unbelief, \V{14} and the grace of our Lord overflowed for me with the faith and love that are in Christ Jesus. \V{15} The saying is trustworthy and deserving of full acceptance, that Christ Jesus came into the world to save sinners, of whom I am the foremost. \V{16} But I received mercy for this reason, that in me, as the foremost, Jesus Christ might display his perfect patience as an example to those who were to believe in him for eternal life. \V{17} To the King of the ages, immortal, invisible, the only God, be honor and glory forever and ever. Amen.}

Science Fact \#1 - ``Total Reflection''
This is a situation where `light waves' are reflected in all directions so that you can no longer see a specific object at all. Try this experiment: Put a coin on a table. Now set a clear jar on top of the coin right side up. Pour pure, clean water into the jar and put the lid on. The coin will seem to have disappeared. No matter how hard you try to look through the water, it's as if the coin is not there. That's what happens when God makes us ``pure and clean.'' He no longer 'sees' our sin and we can enjoy our relationship with Him.

\clearpage
\section{Fourth Day (Tuesday): Gratitude}

\noindent Light the top candle then the bottom candle, then the next highest, and finally the second lowest.  We light the top candle as God is the greatest, the bottom as our sin is the worst, the second highest as God's grace reaches down to us, and the second lowest as our gratitude rises up toward God.

\Scripture{}{ESV}{
}


\noindent Pray together


\noindent Sing \emph{}

%\inputSong{../songs/.tex}


\noindent Read

\Scripture{}{ESV}{}

\noindent Sing \emph{Psalm 51}

\inputSong{../songs/Psalm51.tex}

\noindent Pray


put pictures in

\clearpage
\section{Week 5: Thanksgiving}

scrapbook your pictures and notes during the day.  After dinner, light all five candles and sing aaa. pray. share pages.  sing aaa . closing prayer of thanksgiving.




%\Scripture{Jude 24-25}{KJV}{Now unto him that is able to keep you from falling, and to present you faultless before the presence of his glory with exceeding joy, To the only wise God our Saviour, be glory and majesty, dominion and power, both now and ever. Amen.}
