\chapter{First Week of Advent}

\section{The Hope of Immediate Fulfilment}
\begin{quote}
14  And the LORD God said unto the serpent, Because thou hast done this, thou art cursed above all cattle, and above every beast of the field; upon thy belly shalt thou go, and dust shalt thou eat all the days of thy life:
15  And I will put enmity between thee and the woman, and between thy seed and her seed; it shall bruise thy head, and thou shalt bruise his heel.
\begin{flushright}Genesis 3:14-15\end{flushright}\end{quote}


\begin{quote}
1  And Adam knew Eve his wife; and she conceived, and bare Cain, and said, I have gotten a man from the LORD.
2  And she again bare his brother Abel. And Abel was a keeper of sheep, but Cain was a tiller of the ground.

3  And in process of time it came to pass, that Cain brought of the fruit of the ground an offering unto the LORD.
4  And Abel, he also brought of the firstlings of his flock and of the fat thereof. And the LORD had respect unto Abel and to his offering:
5  But unto Cain and to his offering he had not respect. And Cain was very wroth, and his countenance fell.

6  And the LORD said unto Cain, Why art thou wroth? and why is thy countenance fallen?
7  If thou doest well, shalt thou not be accepted? and if thou doest not well, sin lieth at the door. And unto thee shall be his desire, and thou shalt rule over him.

8  And Cain talked with Abel his brother: and it came to pass, when they were in the field, that Cain rose up against Abel his brother, and slew him.

9  And the LORD said unto Cain, Where is Abel thy brother? And he said, I know not: Am I my brother’s keeper?
10  And he said, What hast thou done? the voice of thy brother’s blood crieth unto me from the ground.
11  And now art thou cursed from the earth, which hath opened her mouth to receive thy brother’s blood from thy hand;
12  When thou tillest the ground, it shall not henceforth yield unto thee her strength; a fugitive and a vagabond shalt thou be in the earth.

13  And Cain said unto the LORD, My punishment is greater than I can bear.
14  Behold, thou hast driven me out this day from the face of the earth; and from thy face shall I be hid; and I shall be a fugitive and a vagabond in the earth; and it shall come to pass, that every one that findeth me shall slay me.
15  And the LORD said unto him, Therefore whosoever slayeth Cain, vengeance shall be taken on him sevenfold. And the LORD set a mark upon Cain, lest any finding him should kill him.
\begin{flushright}Genesis 4:1-15\end{flushright}\end{quote}

\section{The Need for a Prophet}

\begin{quote}
18  And all the people saw the thunderings, and the lightnings, and the noise of the trumpet, and the mountain smoking: and when the people saw it, they removed, and stood afar off.
19  And they said unto Moses, Speak thou with us, and we will hear: but let not God speak with us, lest we die.
20  And Moses said unto the people, Fear not: for God is come to prove you, and that his fear may be before your faces, that ye sin not.
21  And the people stood afar off, and Moses drew near unto the thick darkness where God was.
\begin{flushright}Exodus 20:18-21\end{flushright}\end{quote}


\begin{quote}
15  The LORD thy God will raise up unto thee a Prophet from the midst of thee, of thy brethren, like unto me; unto him ye shall hearken;
16  According to all that thou desiredst of the LORD thy God in Horeb in the day of the assembly, saying, Let me not hear again the voice of the LORD my God, neither let me see this great fire any more, that I die not.
17  And the LORD said unto me, They have well spoken that which they have spoken.
18  I will raise them up a Prophet from among their brethren, like unto thee, and will put my words in his mouth; and he shall speak unto them all that I shall command him.
19  And it shall come to pass, that whosoever will not hearken unto my words which he shall speak in my name, I will require it of him.
20  But the prophet, which shall presume to speak a word in my name, which I have not commanded him to speak, or that shall speak in the name of other gods, even that prophet shall die.
21  And if thou say in thine heart, How shall we know the word which the LORD hath not spoken?
22  When a prophet speaketh in the name of the LORD, if the thing follow not, nor come to pass, that is the thing which the LORD hath not spoken, but the prophet hath spoken it presumptuously: thou shalt not be afraid of him.
\begin{flushright}Deuteronomy 18:15-22\end{flushright}\end{quote}


\begin{quote}
5  So Moses the servant of the LORD died there in the land of Moab, according to the word of the LORD.
6  And he buried him in a valley in the land of Moab, over against Bethpeor: but no man knoweth of his sepulchre unto this day.
7  And Moses was an hundred and twenty years old when he died: his eye was not dim, nor his natural force abated.
8  And the children of Israel wept for Moses in the plains of Moab thirty days: so the days of weeping and mourning for Moses were ended.

9  And Joshua the son of Nun was full of the spirit of wisdom; for Moses had laid his hands upon him: and the children of Israel hearkened unto him, and did as the LORD commanded Moses.
10  And there arose not a prophet since in Israel like unto Moses, whom the LORD knew face to face,
11  In all the signs and the wonders, which the LORD sent him to do in the land of Egypt to Pharaoh, and to all his servants, and to all his land,
12  And in all that mighty hand, and in all the great terror which Moses shewed in the sight of all Israel.
\begin{flushright}Deuteronomy 34:5-12\end{flushright}\end{quote}


\begin{quote}
43  The day following Jesus would go forth into Galilee, and findeth Philip, and saith unto him, Follow me.
44  Now Philip was of Bethsaida, the city of Andrew and Peter.
45  Philip findeth Nathanael, and saith unto him, We have found him, of whom Moses in the law, and the prophets, did write, Jesus of Nazareth, the son of Joseph.
46  And Nathanael said unto him, Can there any good thing come out of Nazareth? Philip saith unto him, Come and see.
47  Jesus saw Nathanael coming to him, and saith of him, Behold an Israelite indeed, in whom is no guile!
48  Nathanael saith unto him, Whence knowest thou me? Jesus answered and said unto him, Before that Philip called thee, when thou wast under the fig tree, I saw thee.
49  Nathanael answered and saith unto him, Rabbi, thou art the Son of God; thou art the King of Israel.
50  Jesus answered and said unto him, Because I said unto thee, I saw thee under the fig tree, believest thou? thou shalt see greater things than these.
51  And he saith unto him, Verily, verily, I say unto you, Hereafter ye shall see heaven open, and the angels of God ascending and descending upon the Son of man.
\begin{flushright}John 1:43-51\end{flushright}\end{quote}

\begin{quote}
17  And now, brethren, I wot that through ignorance ye did it, as did also your rulers.
18  But those things, which God before had shewed by the mouth of all his prophets, that Christ should suffer, he hath so fulfilled.
19  Repent ye therefore, and be converted, that your sins may be blotted out, when the times of refreshing shall come from the presence of the Lord;
20  And he shall send Jesus Christ, which before was preached unto you:
21  Whom the heaven must receive until the times of restitution of all things, which God hath spoken by the mouth of all his holy prophets since the world began.
22  For Moses truly said unto the fathers, A prophet shall the Lord your God raise up unto you of your brethren, like unto me; him shall ye hear in all things whatsoever he shall say unto you.
23  And it shall come to pass, that every soul, which will not hear that prophet, shall be destroyed from among the people.
24  Yea, and all the prophets from Samuel and those that follow after, as many as have spoken, have likewise foretold of these days.
25  Ye are the children of the prophets, and of the covenant which God made with our fathers, saying unto Abraham, And in thy seed shall all the kindreds of the earth be blessed.
26  Unto you first God, having raised up his Son Jesus, sent him to bless you, in turning away every one of you from his iniquities.
\begin{flushright}Acts 3:17-26\end{flushright}\end{quote}