\chapter{Christmas}


















\section{The Seed of the Woman}
Reader: Keith Evan Schubert

Genesis 3:9-15, 12:1-7, %49:8-12, 
Numbers 24:15-19

(Right) Mary Did You Know


\section{Isaiah's Prophesy}

Isaiah 7:14, 9:1-7, 11:1-10

(123) O Come, O Come, Emmanuel

\section{The Saviour Prefigured}

Genesis 49:8-12, Jeremiah 31:15-17, Micah 5:1-6

(145) O Come All Ye Faithful

\section{Announcement}

Matthew 1:18-25, Luke 1:26-56

(137) What Child is This?

\section{The King's Comming}

Isaiah 49:1-13, Luke 2:1-20

(132) Angels We Have Heard on High

\section{Three Magi}

Matthew 2:1-23

(166) We Three Kings

\section{Praise in the Temple}

Luke 2:21-40

(125) Joy to the World


\pagebreak


Mary, Did You Know?

Mary, did you know that your baby boy
would one day walk on water?
Mary, did you know that your baby boy
would save our sons and daughters?
Did you know that your baby boy
has come to make you new;
and this child that you delivered
will soon deliver you?

Mary, did you know that your baby boy
would give sight to the blind man?
Mary, did you know that your baby boy
would calm a storm with his hand?
Did you know that your baby boy
has walked where angels trod?
And, when you kissed your little baby
you've kissed the face of God?
Oh, Mary, did you know?
Mary, did you know?

The blind will see, the deaf will hear
the dead will live again.
The lame will leap,
the dumb will speak the praises of the Lamb.

Oh, Mary, did you know?
that your baby boy is Lord of all creation?
Mary, did you know that your baby boy
would one day rule the nations?
Did you know that your baby boy
was Heaven's perfect Lamb?
And, the sleeping child you're holding is the great I Am?
Oh, Mary, did you know?
So long ago?


\copyright 1991 Word Music/Rufus Music ASCAP Mark Lowry \& Buddy Greene




Therefore the Lord himself shall give you a sign; Behold, a virgin shall
conceive, and bear a son, and shall call his name Immanuel. (Isaiah 7:14).

Nevertheless the dimness shall not be such as was in her vexation, when
at the first he lightly afflicted the land of Zebulun and the land of Naphtali,
and afterward did more grievously afflict her by the way of the sea, beyond
Jordan, in Galilee of the nations. The people that walked in darkness have
seen a great light: they that dwell in the land of the shadow of death,
upon them hath the light shined. Thou hast multiplied the nation, and not
increased the joy: they joy before thee according to the joy in harvest,
and as men rejoice when they divide the spoil. For thou hast broken the
yoke of his burden, and the staff of his shoulder, the rod of his oppressor,
as in the day of Midian. For every battle of the warrior is with confused
noise, and garments rolled in blood; but this shall be with burning and
fuel of fire. For unto us a child is born, unto us a son is given: and
the government shall be upon his shoulder: and his name shall be called
Wonderful, Counsellor, The mighty God, The everlasting Father, The Prince
of Peace. Of the increase of his government and peace there shall be no
end, upon the throne of David, and upon his kingdom, to order it, and to
establish it with judgment and with justice from henceforth even for ever.
The zeal of the LORD of hosts will perform this. (Isaiah 9:1-7).

And there shall come forth a rod out of the stem of Jesse, and a Branch
shall grow out of his roots: And the spirit of the LORD shall rest upon
him, the spirit of wisdom and understanding, the spirit of counsel and
might, the spirit of knowledge and of the fear of the LORD; And shall make
him of quick understanding in the fear of the LORD: and he shall not judge
after the sight of his eyes, neither reprove after the hearing of his ears:
But with righteousness shall he judge the poor, and reprove with equity
for the meek of the earth: and he shall smite the earth with the rod of
his mouth, and with the breath of his lips shall he slay the wicked. And
righteousness shall be the girdle of his loins, and faithfulness the girdle
of his reins. The wolf also shall dwell with the lamb, and the leopard
shall lie down with the kid; and the calf and the young lion and the fatling
together; and a little child shall lead them. And the cow and the bear
shall feed; their young ones shall lie down together: and the lion shall
eat straw like the ox. And the sucking child shall play on the hole of
the asp, and the weaned child shall put his hand on the cockatrice' den.
They shall not hurt nor destroy in all my holy mountain: for the earth
shall be full of the knowledge of the LORD, as the waters cover the sea.
And in that day there shall be a root of Jesse, which shall stand for an
ensign of the people; to it shall the Gentiles seek: and his rest shall
be glorious. (Isaiah 11:1-10).

123 O Come, O Come, Emmanuel

Michah 5:2
145 O Come All Ye Faithful


Listen, O isles, unto me; and hearken, ye people, from far; The LORD hath
called me from the womb; from the bowels of my mother hath he made mention
of my name. And he hath made my mouth like a sharp sword; in the shadow
of his hand hath he hid me, and made me a polished shaft; in his quiver
hath he hid me; And said unto me, Thou art my servant, O Israel, in whom
I will be glorified. Then I said, I have laboured in vain, I have spent
my strength for nought, and in vain: yet surely my judgment is with the
LORD, and my work with my God. And now, saith the LORD that formed me from
the womb to be his servant, to bring Jacob again to him, Though Israel
be not gathered, yet shall I be glorious in the eyes of the LORD, and my
God shall be my strength. And he said, It is a light thing that thou shouldest
be my servant to raise up the tribes of Jacob, and to restore the preserved
of Israel: I will also give thee for a light to the Gentiles, that thou
mayest be my salvation unto the end of the earth. Thus saith the LORD,
the Redeemer of Israel, and his Holy One, to him whom man despiseth, to
him whom the nation abhorreth, to a servant of rulers, Kings shall see
and arise, princes also shall worship, because of the LORD that is faithful,
and the Holy One of Israel, and he shall choose thee. Thus saith the LORD,
In an acceptable time have I heard thee, and in a day of salvation have
I helped thee: and I will preserve thee, and give thee for a covenant of
the people, to establish the earth, to cause to inherit the desolate heritages;
That thou mayest say to the prisoners, Go forth; to them that are in darkness,
Shew yourselves. They shall feed in the ways, and their pastures shall
be in all high places. They shall not hunger nor thirst; neither shall
the heat nor sun smite them: for he that hath mercy on them shall lead
them, even by the springs of water shall he guide them. And I will make
all my mountains a way, and my highways shall be exalted. Behold, these
shall come from far: and, lo, these from the north and from the west; and
these from the land of Sinim. Sing, O heavens; and be joyful, O earth;
and break forth into singing, O mountains: for the LORD hath comforted
his people, and will have mercy upon his afflicted. (Isaiah 49:1-13).

132 Angels We Have Heard on High

133 Hark! the Herald Angels Sing

137 What Child is This?

147 Silent Night! Holy Night!

166 We Three Kings

125 Joy to the World

