\chapter{Jesus at Hanukkah}

Read John 10:22-42

The Feast of Dedication is the old name for Hanukkah, or the Feast of Lights.  It commemorates the rededication of the temple in 164 BC by Judas Maccabeus, after the desecration by Antiochus Epiphanes.  Given the timing it seemed an appropriate place to study.

When is Hanukkah celebrated?  What does the text say?  Since Hanukkah happens the same time every year (25 Kislev), why note that it was winter?  Where is Jesus?  Does it really matter?  What is John trying to get across in verse 24?  Do the Jews have an agenda?  How can we be sure?  Did the Romans allow capitol punishment?  How did the Jews think they could get away with stoning Jesus?  Could the Romans stop an uprising in the temple quickly?  Read Acts 21:27-36.  Where were the Roman barracks? Where was Jesus with respect to them?  Look at a picture of the temple grounds and read John 10:31.  Does anything seem odd?  Why did the mob take Paul outside?  What can be concluded?  Since there were no lose rocks in the temple grounds people would have had to have brought them to stone Jesus and pulled them at the appropriate time.

How does Jesus start His answer to their first question?  What does Jesus say the Jews do not believe?  Why don't they believe?  How does a believer respond?  What is the gift and the guarantee?  How does Jesus end the answer?  How does it correspond to the question?

How do the Jews respond to Jesus' answer?  What is the purpose of Jesus' question, and the Jews answer?  As strange as it may sound, many hold that Jesus never claimed to be God.  Do the Jews agree?  Does Jesus' reply, seem unusual to you?  What does the argument appear to be?  Read Psalm 82.  What is the context and subject of Psalm 82?  How does the Psalm fit the situation?    How does Jesus end His statement?  Does this support the Arminian position?  Did they believe?  Why not?  What is Jesus really doing here?

How do verses 40-42 compare with the preceding passage?  What can we get from it?
